validateHOT - an R package for holdout task validation and market simulations

### 2024-03-03 paper/paper.Rmd
shortening paper - 240303

For the following example, we assume that the user conducted an anchored MaxDiff analysis with 10 items (\texttt{\color{purple}opts}) and now wants to find the best assortment with a size of 3. As a threshold (\texttt{\color{purple}none}), the user uses the anchor (no-buy alternative).

@@

Finally, we can also display the attributes importance scores. Therefore, we need to define the attribute levels as well as the coding of the attributes.

>>>>

For the following example, let's assume that the user conducted an anchored MaxDiff analysis with 10 items (\texttt{\color{purple}opts}) and now wants to find the best assortment with a size of 3 items. The user uses the anchor (no-buy alternative) as a threshold.

@@

We can also display the attributes importance scores. Therefore, we need to define the attribute levels as well as the coding of the attributes.
